---
title: "Assignment 6"
author: "Lauren Thomson"
date: "2023-01-23"
output: 
  prettydoc::html_pretty:
      theme: cayman
      highlight: github
---

## 1. Examine the structure of the iris data set. How many observations and variables are in the data set?

```{r}
library(dplyr)
glimpse(iris)

## There are 150 observations and 5 variables. 
```
## 2. Create a new data frame iris1 that contains only the species virginica and versicolor with sepal lengths longer than 6 cm and sepal widths longer than 2.5 cm. How many observations and variables are in the data set?

```{r}
is.na(iris)
iris1 <- filter(iris, Species %in% c("virginica", "versicolor") & Sepal.Length > 6 & Sepal.Width > 2.5)
glimpse(iris1)

# 56 observations meet this criteria 
```
## 3. Now, create a iris2 data frame from iris1 that contains only the columns for Species, Sepal.Length, and Sepal.Width. How many observations and variables are in the data set?

```{r}
iris2 <- select(iris1, -(Petal.Length:Petal.Width))
glimpse(iris2)
```
## 4. Create an iris3 data frame from iris2 that orders the observations from largest to smallest sepal length. Show the first 6 rows of this data set.

```{r}
iris3 <- arrange(iris2, by=desc(Sepal.Length))
head(iris3)
```
## 5. Create an iris4 data frame from iris3 that creates a column with a sepal area (length * width) value for each observation. How many observations and variables are in the data set?

```{r}
iris4 <- mutate(iris3, Sepal.Area = Sepal.Length * Sepal.Width)
glimpse(iris4)

# Observations: 56, Variables: 4  
```
## 6. Create the variable irisTab that shows the average sepal length, the average sepal width, and the sample size of the entire iris4 data frame and print irisTab.

```{r}

irisTab <- summarize(iris4, mean.Sepal.Length = mean(Sepal.Length), mean.Sepal.Width = mean(Sepal.Width), TotalNumbers = n())
print(irisTab)

```
## 7. Finally, create iris5 that calculates the average sepal length, the average sepal width, and the sample size for each species of in the iris4 data frame and print iris5.

```{r}
iris4 %>% 
  group_by(Species) %>%
  summarize(mean.Sepal.Length = mean(Sepal.Length), mean.Sepal.Width = mean(Sepal.Width), TotalNumbers = n())
```

## 8. Rework all of your previous statements (except for irisTab) into an extended piping operation that uses iris as the input and generates irisFinal as the output.

```{r}
# 2. iris1

finaliris <- iris %>%
  filter(Species %in% c("virginica", "versicolor") & Sepal.Length > 6 & Sepal.Width > 2.5) %>%
  select(-(Petal.Length:Petal.Width)) %>%
  arrange(by=desc(Sepal.Length)) %>%
   mutate(Sepal.Area = Sepal.Length * Sepal.Width) %>%
  group_by(Species) %>%
 summarize(mean.Sepal.Length = mean(Sepal.Length), mean.Sepal.Width = mean(Sepal.Width), mean.Sepal.Area = mean(Sepal.Area), TotalNumbers = n())
  
print(finaliris)





```



