---
title: "Assignment 7"
author: "Lauren Thomson"
date: "2023-01-24"
output: 
  prettydoc::html_pretty:
      theme: cayman
      highlight: github
---
### 1. Using the built-in starwars data set in the dplyr package, create a new tibble with the following modifications:

```{r}
library(dplyr)
#It only includes the species that have more than 1 individual represented in the data set. (hint: first use dplyr to summarize the number of individuals per species in the data frame; then create a vector/tibble of those names; subset the species that are included in that vector)
data(starwars)
sw_species <- starwars %>%
  group_by(species) %>%
  summarize(TotalNumber=n()) %>%
  filter(TotalNumber > 1)

final <- starwars %>%
  filter(species %in% sw_species$species)

 
final_2 <- final %>% 
  select(-(films:starships))


#It only includes the columns that are not of type list (hint: use glimpse to check)

glimpse(final_2)

```
### 2. Clean your data set: only include observations/rows that do not have an NA in the height column. Then, use dplyr to print a summary table showing the mean, median, and standard deviation of height for each species.
```{r}
glimpse(final_2)
finalClean <- final_2[complete.cases(final_2 [,2]), ]



library(dplyr)
finalStats <- finalClean %>%
  group_by(species)%>%
  summarize(MeanHeight = mean(height), MedianHeight = median(height), StDvHeight = sd(height))

print(finalStats)
```
### 3. 

```{r}
library(ggplot2)
library(ggthemes)
library(patchwork)
library(viridis)

cols <- viridis(9, option = "viridis") 
species_height<-  ggplot(data = finalClean, aes(x=species, y=height, fill = species)) + 
  geom_boxplot() + 
  xlab("Species") +
  ylab("Height cm") + 
  theme_minimal() +
  geom_text(x=9, y=230, label="p=1.2E-0.5")+
  scale_fill_manual(values=cols) 

print(species_height)
```


### Challenge Question: overlay the data points onto the box plots.

```{r}
cols <- viridis(9, option = "viridis") 
species_height_overlay <-  ggplot(data = finalClean, aes(x=species, y=height, fill = species)) + 
  geom_boxplot() + 
  xlab("Species") +
  ylab("Height cm") + 
  theme_minimal() +
  geom_text(x=9, y=230, label="p=1.2E-0.5")+
  scale_fill_manual(values=cols) +
  geom_point(size=2, shape = 25, aes(color = gender))

print(species_height_overlay)

```

### 4. Using the same or a different built-in data set, create at least one additional plot. 

```{r}
data(iris)
glimpse(iris)
anyNA(iris)

sepal_variation <- ggplot(data = iris, aes(x=Sepal.Width, y=Sepal.Length)) + 
  geom_point(size=4, shape = 25, color = "magenta", fill= "forestgreen") + 
  xlab("Sepal.Width cm") +
  ylab("Sepal.Length cm") + 
  theme_minimal() +
  geom_smooth(method = "lm", se = F) +
  scale_fill_manual(values=cols)

print(sepal_variation)
```

### 5 

```{r}
(sepal_variation + species_height )/ species_height_overlay


```





