---
title: "Assignment 9"
author: "Lauren Thomson"
date: "2023-01-30"
output: 
  prettydoc::html_pretty:
      theme: cayman
      highlight: github
---

## 1. Using a for loop and an if statement, write a function to calculate the number of zeroes in a numeric vector. Before entering the loop, set up a vector of integers with some zero values

```{r}
vect <- sample(rep(0:1, times=4))
varcounter <- 0 
zeros <- function(vector){
  for (i in 1:length(vector)){
  if (vect[i]==0) {varcounter <- varcounter + 1} 
  }
  return(varcounter)
}
zeros(vect)
```
 
## 2. Write a function that takes as input two integers representing the number of rows and columns in a matrix. The output is a matrix of these dimensions in which each element is the product of the row number x the column number. 

```{r}
buildm <- function (rows, columns){
  matrix <- matrix(data=NA, nrow= rows, ncol = columns)
  for(i in 1:rows){
    for(j in 1:columns){
      matrix[i,j] <- i * j
  }
  }  
  return (matrix)
}
buildm(rows=5, columns=4)

```


## 3. Use a for loop to repeat your previous functions from Weekly Assignment 2 (which simulate a data frame and extract a p-value) 100 times. Store the results in a data frame that has 1 column indicating the replicate number and 1 column for the p-values (a total of 2 columns and 100 rows).

```{r}
df_pvalue <- function(mean1=10, sd1 = 1, n=25, mean2=45, sd2 = 2){
  data_frame_p <- data.frame("Iteration", "P_Value") #making empty data frame
  for (i in 1:100) {
   Type = c(rep(x = "Control", times = n), rep( x = "Treatment", times = n))
   Value = c(rnorm(n, mean = mean1, sd = sd1), rnorm(n, mean = mean1, sd= sd2))
   data_frame <- data.frame(Type, Value, stringsAsFactors = F)
    test <- aov(Value ~ Type, data=data_frame) #performing aov
    testSummary <- summary(test) #saving summary as variable
    p_value <- testSummary[[1]][["Pr(>F)"]][1] #indexing pValue
    data_frame_p <- rbind(data_frame_p, c(i, p_value)) #adding each iteration to old dataframe
    mean1 <- mean1 + 1 #changing data values (same as with below)
    sd1 <- sd1 + 1
    n <- n +1 
    mean2 <- mean2 + 1 
    sd2 <- sd2 + 1 
   }
  return (data_frame_p)
}
df_pvalue()

   
```
 