---
title: "Weekly Assignment 2"
author: "Lauren Thomson"
date: "2023-01-23"
output: 
  prettydoc::html_pretty:
      theme: cayman
      highlight: github
---

## Creating Functions

### 1. Create a function that returns a data frame with 2 columns (named “Type” and “Value”) and 50 rows/observations.

```{r}

######################
# Function: dFrame 
# Input: Two means of random normal numbers
# output data frame with 2 columns, Type and Value 
#-------------------------------
dFrame <- function(a=10, b=45){
  Type = c(rep(x = "Control", times = 25), rep( x = "Treatment", times = 25))
  Value = c(rnorm(25, mean = a, sd=1), rnorm(25, mean = b, sd=2))
  data_frame<-data.frame(Type, Value, stringsAsFactors = F)
  return(data_frame)
} 
                 
```
### 2. Save your new function’s output as a variable, and view the first 6 rows of the data frame.
```{r}
data_50 <- dFrame(a=10, b=45) #saving funtion as a variable

head(data_50) #looking at first 6 lines of data frame
```

### 3. Write a line of code that displays a summary of your ANOVA

```{r}
summary(aov(Value~Type, data = data_50))
```
### 4. Create a function that uses a data frame as its input and returns only the p-value of an ANOVA summary table

```{r}

##############
# Function: dFrame_stats 
# Input: data frame with two columns 
# Reutrn: p-value of an ANOVA summary table
#------------------
dFrame_stats <- function(df){
    x <- df[,1]
    y <- df[,2]
    stats<-summary(aov(y~x, data = df))
    stats_list <- unlist(stats)
    p_value<-stats_list[9]
    return(p_value)
}

print(dFrame_stats(data_50))
```

